\bf A Concise Survey on Statistical Analysis in Bike Lane Research

### 2023-11-11 Manuscript/Manuscript.tex
worked on methods section and identfying results

@@

2, 4, 5 Binary Probit Regression Analysis.

@@

3. The paper from \citet{3Teixeira2020} uses Multipple Level Logistic Regression to analyze the impact of cycling in various cities with different cycling infrastructure on stress markers. This analysis resulted in the data shown in Table ~\ref{fig:stress}.
\begin{figure}[tbp]
    \centering
    \includegraphics[width=0.5\textwidth]{stresstable2.jpeg}
    \caption{Distribution of Stress by City from Teixeira Study}
    \label{fig:stress}
\end{figure}

@@

>>>>

To conduct this comprehensive survey of statistical analyses on bike lanes, a search was conducted of academic databases such as Science Direct, ProQuest, MDPI, and PubMed. These searches were conducted through the University of Connecticut library of Databases to ensure they were papers that were a able to be accessed. Specific terms were used including "bike lane", "statistical analysis", and "cycling infrastructure" in order to identify relevant papers. The date range for literature was defined as 2012 to the present, upon evaluation of typical date range of the available literature. \par

\subsection{Criteria of Inclusion and Exclusion}
\label{sec:inc}

Literature was included in the survey if it met these criteria:

\begin{enumerate}
        \item Whether the paper held sufficient statistical analysis on the topic of bike lanes. 
        \item Being publicized in a peer-reviewed, reputable journal.
        \item Availability of paper for access using University of Connecticut student status. 
\end{enumerate}

\subsection{Data}
\label{sec:data}

The data in this survey paper is the types of statistical analyses conducted by the identified literature from method given above. A selection of eleven papers resulted from this, and the approach used to identify relevant data from the papers to be discussed in the survey paper was done as follows. The specific type of statistical analysis conducted in the paper was identified. Alongside the method and variables used by the researchers in the study. The results from the data collection are displayed in ~\ref{sec:results}.

@@

2, 4, 5, 7 Binary Probit Regression Analysis.

@@

3, 10. The paper from \citet{3Teixeira2020} uses Multipple Level Logistic Regression to analyze the impact of cycling in various cities with different cycling infrastructure on stress markers. This analysis resulted in the data shown in Table ~\ref{fig:stress}.
\begin{figure}[tbp]
    \centering
    \includegraphics[width=0.5\textwidth]{stresstable2.jpeg}
    \caption{Distribution of Stress by City from Teixeira Study}
    \label{fig:stress}
\end{figure}

@@

\subsection{Zero-inflated Poisson regression mode}
\label{sec:pois}

paper 8, 9
